\LaTeXe\ guide for the Journal of Functional Programming

### 2019-04-25 papers/jfp/8-engineering.tex
Rearrange TODOs

One tempting way of modelling non-determinism is to enrich \hs{Tasks} from
\hs{Applicative} or \hs{Monad} to \hs{Alternative} or \hs{MonadPlus},
respectively. More concretely, the following task description corresponds to
a spreadsheet with the formula \cmd{B1 = A1 + RANDBETWEEN(1,2)}.

\begin{minted}[xleftmargin=10pt]{haskell}
sprsh3 :: Tasks MonadPlus String Integer
sprsh3 "B1"@\,@=@\,@Just $ Task $ \fetch -> (+) <$> fetch "A1" <*> (pure@\,@1 <|> pure@\,@2)
sprsh3 _   @\,@=@\,@Nothing
\end{minted}
\vspace{1mm}

\noindent
Such tasks can be modelled in our framework by adjusting the correctness
definition (\S\ref{sec-build-correctness}): instead of requiring that the
\hs{result}ing value \emph{equals} the one obtained by recomputing the \hs{task}:
\[
\hs{getValue}~\hs{k}~\hs{result}~\hs{==}~\hs{compute}~\hs{task}~\hs{result} %\text{,}
\]
\noindent
we now require that \hs{result} contains \emph{one possible result of
recomputing} the \hs{task}:
\[
\hs{getValue}~\hs{k}~\hs{result}~\hs{`elem`}~\hs{computeND}~\hs{task}~\hs{result} %\text{,}
\]
where
\hs{computeND}~\hs{::}~\hs{Task}~\hs{MonadPlus}~\hs{k}~\hs{v}~\hs{->}~\hs{Store}~\hs{i}~\hs{k}~\hs{v}~\hs{->}~\hs{[@@v]}
returns the list of all possible results of the \hs{task} instead of just one
value (`ND' stands for `non-deterministic').

>>>>

One tempting way of modelling non-determinism is to enrich \hs{Tasks} from
\hs{Applicative} or \hs{Monad} to \hs{Alternative} or \hs{MonadPlus},
respectively. Here is a task description corresponding to a spreadsheet with the
formula \cmd{B1 = A1 + RANDBETWEEN(1,2)}:

\begin{minted}[xleftmargin=10pt]{haskell}
sprsh3 :: Tasks MonadPlus String Integer
sprsh3 "B1" = Just $ Task $ \fetch -> (+) <$> fetch "A1"
                                          <*> (pure 1 <|> pure 2)
sprsh3 _    = Nothing
\end{minted}
\vspace{1mm}

\noindent
Such tasks can be modelled in our framework by adjusting the correctness
definition~(\S\ref{sec-build-correctness}), where instead of requiring that the
\hs{result}ing value \emph{equals} the one obtained by recomputing the \hs{task}:
\[
\hs{getValue}~\hs{k}~\hs{result}~\hs{==}~\hs{compute}~\hs{task}~\hs{result} %\text{,}
\]
\noindent
we now require that \hs{result} contains \emph{one possible result of
recomputing} the \hs{task}:
\[
\hs{getValue}~\hs{k}~\hs{result}~\hs{`elem`}~\hs{computeND}~\hs{task}~\hs{result} %\text{,}
\]
where
\hs{computeND}~\hs{::}~\hs{Task}~\hs{MonadPlus}~\hs{k}~\hs{v}~\hs{->}~\hs{Store}~\hs{i}~\hs{k}~\hs{v}~\hs{->}~\hs{[@@v]}
returns the list of all possible results of the \hs{task} instead of just one
value (`ND' stands for `non-deterministic').

\todo{AM}{Show implementation of \hs{computeND}}.
